NFC and burnout in teachers - A replication and extension study

### 2021-08-31 Manuscript/Manuscript.Rmd
table knitting fully functional

#install.packages("here")       # easy file referencing
#install.packages("tidyverse")  # plotting and managing data
#install.packages("lavaan")     # for structural equation modelling
#install.packages("psych")      # Cronbach's Alpha and such
#install.packages("MVN")        # Mardia's test and such
#install.packages("MBESS")      # MacDonald's Omega
#install.packages("Hmisc")      # for correlations with p-values
#install.packages("kableExtra") # for great tables
#install.packages("knitr")      # for knitting documents and tables

@@

  for (i in 1:nrow(data)) {
    score_data[i,c(2:ncol(score_data))] <- c(rowSums(mbi[i,]),
                                             rowSums(mbi[i,keylist$mbi_ee]), rowSums(mbi[i,keylist$mbi_dp]), rowSums(mbi[i,keylist$mbi_rpe]),
                                             rowSums(erq[i,]),
                                             rowSums(erq[i,keylist$erq_supp]), rowSums(erq[i,keylist$erq_reap]),
                                             rowSums(scs[i,]),
                                             rowSums(ncs[i,]),
                                             rowSums(ncs[i,keylist$parcel1]), rowSums(ncs[i,keylist$parcel2]), rowSums(ncs[i,keylist$parcel3]), rowSums(ncs[i,keylist$parcel4]),
                                             rowSums(dth[i,]),
                                             dth[i,1], dth[i,2], dth[i,3],
                                             rowSums(dtl[i,]),
                                             dtl[i,1], dtl[i,2], dtl[i,3],
                                             rowSums(drf[i,]),
                                             drf[i,1], drf[i,2], drf[i,3],
                                             rowSums(covb[i,]))
  }
```

@@

    # set row and column names for better table printing
    row.names(corr_no_drr) <- c("MBI Score","MBI EE","MBI DP","MBI RPE","ERQ","ERQ Suppression","ERQ Reappraisal","Self Control","NFC","Covid-19 Burden")
    colnames(corr_no_drr) <- c("MBI","MBI EE","MBI DP","MBI RPE","ERQ","ERQ S","ERQ R","SCS","NFC","COV")

@@

```{r desc_table, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

  desc_table <-
  kbl(corr_no_drr,
      booktabs = T,
      align = rep("r",11)) %>%
    kable_styling(latex_options = "striped", position = "center", full_width = T, font_size = 10) %>%
    column_spec(2, italic = corr_onestar$mbi|corr_twostars$mbi, bold = corr_threestars$mbi|corr_twostars$mbi) %>%
    column_spec(3, italic = corr_onestar$mbi_ee|corr_twostars$mbi_ee, bold = corr_threestars$mbi_ee|corr_twostars$mbi_ee) %>%
    column_spec(4, italic = corr_onestar$mbi_dp|corr_twostars$mbi_dp, bold = corr_threestars$mbi_dp|corr_twostars$mbi_dp) %>%
    column_spec(5, italic = corr_onestar$mbi_rpe|corr_twostars$mbi_rpe, bold = corr_threestars$mbi_rpe|corr_twostars$mbi_rpe) %>%
    column_spec(6, italic = corr_onestar$erq|corr_twostars$erq, bold = corr_threestars$erq|corr_twostars$erq) %>%
    column_spec(7, italic = corr_onestar$erq_supp|corr_twostars$erq_supp, bold = corr_threestars$erq_supp|corr_twostars$erq_supp) %>%
    column_spec(8, italic = corr_onestar$erq_reap|corr_twostars$erq_reap, bold = corr_threestars$erq_reap|corr_twostars$erq_reap) %>%
    column_spec(9, italic = corr_onestar$scs|corr_twostars$scs, bold = corr_threestars$scs|corr_twostars$scs) %>%
    column_spec(10, italic = corr_onestar$ncs|corr_twostars$ncs, bold = corr_threestars$ncs|corr_twostars$ncs) %>%
    column_spec(11, italic = corr_onestar$covb|corr_twostars$covb, bold = corr_threestars$covb|corr_twostars$covb) %>%
    column_spec(2:11, width = "1.5cm") %>%
    footnote(general = "MBI = Maslach Burnout Inventory, MBI EE = Emotional exhaustion subscale, MBI DP = Depersonalisation subscale, MBI RPE = Reduced personal efficacy subscale, ERQ = Emotion Regulation Questionnaire, ERQ S = Suppression subscale, ERQ R = Reappraisal subscale, SCS = Self-Control Scale, NFC = Need for Cognition, COV = Covid-19 Burden. \\\\textit{N} = 180. Italics indicate \\\\textit{p} < .05, italics and bold indicate \\\\textit{p} < .01, bold indicates \\\\textit{p} < .001. Diagonal is Cronbach's Alpha and (in brackets) MacDonald's Omega.")

@@

```{r objective1, echo=FALSE, message=FALSE, warning=FALSE}

@@

```{r objective2, echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}

```
```{r objective2_troubleshooting, echo=FALSE, message=FALSE, warning=FALSE}

  # Plot a big correlational matrix to check for non-linear associations that might have caused the bad model fit
  multicorrplot <- ggpairs(score_data[,c(2,3,4,5,9,10,15,19,23,27)], lower = list(continuous = my_fn))

  # Remove the outlier
  score_data <- score_data[score_data$id != 161, ]

>>>>

#install.packages("here")       # easy file referencing
#install.packages("tidyverse")  # plotting and managing data
#install.packages("lavaan")     # for structural equation modelling
#install.packages("psych")      # Cronbach's Alpha and such
#install.packages("MVN")        # Mardia's test and such
#install.packages("MBESS")      # MacDonald's Omega
#install.packages("Hmisc")      # for correlations with p-values
#install.packages("kableExtra") # for great tables (see haozhu233.github.io/kableExtra/awesome_table_in_pdf.pdf)
#install.packages("knitr")      # for knitting documents and tables

@@

  for (i in 1:nrow(data)) {
    score_data[i,c(2:ncol(score_data))] <- c(rowSums(mbi[i,]),
                                             rowSums(mbi[i,keylist$mbi_ee]), rowSums(mbi[i,keylist$mbi_dp]), rowSums(mbi[i,keylist$mbi_rpe]),
                                             rowSums(erq[i,]),
                                             rowSums(erq[i,keylist$erq_supp]), rowSums(erq[i,keylist$erq_reap]),
                                             rowSums(scs[i,]),
                                             rowSums(ncs[i,]),
                                             rowSums(ncs[i,keylist$parcel1]), rowSums(ncs[i,keylist$parcel2]), rowSums(ncs[i,keylist$parcel3]), rowSums(ncs[i,keylist$parcel4]),
                                             rowSums(dth[i,]),
                                             dth[i,1], dth[i,2], dth[i,3],
                                             rowSums(dtl[i,]),
                                             dtl[i,1], dtl[i,2], dtl[i,3],
                                             rowSums(drf[i,]),
                                             drf[i,1], drf[i,2], drf[i,3],
                                             rowSums(covb[i,]))
  }

  # Plot a big correlational matrix to check for non-linear associations and unexpected outliers
  multicorrplot <- ggpairs(score_data[,c(2,3,4,5,9,10,15,19,23,27)], lower = list(continuous = my_fn))

  # Remove the outlier
  score_data <- score_data[score_data$mbi < 100, ]

@@

    # set row and column names for better table printing
    row.names(corr_no_drr) <- c("MBI","MBI EE","MBI DP","MBI RPE","ERQ","ERQ S","ERQ R","SCS","NFC","COV")
    colnames(corr_no_drr) <- c("MBI","MBI EE","MBI DP","MBI RPE","ERQ","ERQ S","ERQ R","SCS","NFC","COV")

@@

```{r desc_table, echo=FALSE, message=FALSE, warning=FALSE}

  desc_table <-
  kbl(corr_no_drr,
      booktabs = T, # no vertical lines
      escape = F, # correctly print special characters
      align = rep("r",11)) %>% # right aligns the text in every column except for the first
    kable_styling(latex_options = c("striped", "scale_down")) %>%
    column_spec(2, italic = corr_onestar$mbi|corr_twostars$mbi, bold = corr_threestars$mbi|corr_twostars$mbi) %>%
    column_spec(3, italic = corr_onestar$mbi_ee|corr_twostars$mbi_ee, bold = corr_threestars$mbi_ee|corr_twostars$mbi_ee) %>%
    column_spec(4, italic = corr_onestar$mbi_dp|corr_twostars$mbi_dp, bold = corr_threestars$mbi_dp|corr_twostars$mbi_dp) %>%
    column_spec(5, italic = corr_onestar$mbi_rpe|corr_twostars$mbi_rpe, bold = corr_threestars$mbi_rpe|corr_twostars$mbi_rpe) %>%
    column_spec(6, italic = corr_onestar$erq|corr_twostars$erq, bold = corr_threestars$erq|corr_twostars$erq) %>%
    column_spec(7, italic = corr_onestar$erq_supp|corr_twostars$erq_supp, bold = corr_threestars$erq_supp|corr_twostars$erq_supp) %>%
    column_spec(8, italic = corr_onestar$erq_reap|corr_twostars$erq_reap, bold = corr_threestars$erq_reap|corr_twostars$erq_reap) %>%
    column_spec(9, italic = corr_onestar$scs|corr_twostars$scs, bold = corr_threestars$scs|corr_twostars$scs) %>%
    column_spec(10, italic = corr_onestar$ncs|corr_twostars$ncs, bold = corr_threestars$ncs|corr_twostars$ncs) %>%
    column_spec(11, italic = corr_onestar$covb|corr_twostars$covb, bold = corr_threestars$covb|corr_twostars$covb) %>%
    footnote(general = "MBI = Maslach Burnout Inventory, MBI EE = Emotional exhaustion subscale, MBI DP = Depersonalisation subscale, MBI RPE = Reduced personal efficacy subscale, ERQ = Emotion Regulation Questionnaire, ERQ S = Suppression subscale, ERQ R = Reappraisal subscale, SCS = Self-Control Scale, NFC = Need for Cognition, COV = Covid-19 Burden. \\\\textit{N} = 179. Italics indicate \\\\textit{p} < .05, italics and bold indicate \\\\textit{p} < .01, bold indicates \\\\textit{p} < .001. Diagonal is Cronbach's Alpha and (in brackets) MacDonald's Omega.",
             escape = F, # correctly print special characters
             threeparttable = T) # line breaks in the footnote

@@

```{r objective1, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}

@@

```{r objective2, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
